Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-11-22 concurrency/CPP 2024/paper.tex
fix breakage
add CSS concepts

%\usepackage{txfonts}
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{uri}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathpartir}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{cases}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{parcolumns}
\usepackage{iris}
%\usepackage{lstlangcoq}
\usepackage[edges]{forest}
\renewcommand{\lstlistingname}{Figure}

@@

\author{Duc Than Nguyen}
\email{dnguye96@uic.edu}
\orcid{https://orcid.org/0000-0002-6810-897X}
\affiliation{\institution{University of Illinois at Chicago}\streetaddress{}\city{Chicago}\state{IL}\country{USA}\postcode{}}

@@

>>>>

%\usepackage{txfonts}
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{uri}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathpartir}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{cases}
\usepackage{hyperref}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{parcolumns}
%\usepackage{iris}
%\usepackage{lstlangcoq}
\usepackage[edges]{forest}
\renewcommand{\lstlistingname}{Figure}

@@

\author{Duc-Than Nguyen}
\email{dnguye96@uic.edu}
\orcid{https://orcid.org/0000-0002-6810-897X}
\affiliation{\institution{University of Illinois at Chicago}\streetaddress{}\city{Chicago}\state{IL}\country{USA}\postcode{}}

@@

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10011007.10011074.10011099.10011692</concept_id>
	<concept_desc>Software and its engineering~Formal software verification</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Formal software verification}
